Detecci\'on de malas hierbas a trav\'es\\ de t\'ecnicas de redes neuronales convolucionales y visi\'on artificial

### 2017-05-10 PaperBCJ.tex
First Cheng Bibliography

\bibitem{Suarez:Pinero}
R. ~Su\'arez, J. ~Pi\~neiro and J. ~Valladares \emph{Distintos Sistemas De Escarda En Ma\'iz Forrajero} . Vol ~II. \hskip 1em plus
  0.5em minus 0.4em\relax Gij\'on: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.

@@

  \bibitem{Cheng:Mason}
R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.

@@

>>>>

\bibitem{Suarez:Pinero}
R. ~Su\'arez, J. ~Pi\~neiro and J. ~Valladares \emph{Distintos Sistemas De Escarda En Ma\'iz Forrajero} . Vol ~II. \hskip 1em plus
  0.5em minus 0.4em\relax Gij\'on , Spain: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.

@@

  \bibitem{Cheng:Mason}
B.~Cheng and E.T. ~Matson, \emph{A Feature-Based Machine Learning Agent for Automatic Rice and Weed Discrimination} Artificial Intelligence and Soft Computing: 14th International Conference, ICAISC 2015 Part II \hskip 1em plus
  0.5em minus 0.4em\relax Zakopane, Poland , 2015.

@@

\bibliography{•}
